%!TEX root = _DaBa.tex
\chapter{Evaluation}
\label{cha:Evaluation}
In this chapter will be pointed out some difficulties that have been experienced while developing the prototypes for the car2car project.

\section{Communication between mobile platforms}
\label{sec:CommunicationBetweenPlattforms}
One big problem is the compatibility between mobile platforms. The goal was to cover as many platforms as possible. For this project Windows Phone and Android was chosen. iOS was considered at the beginning too, however it uses a proprietary protocol, which is not compatible with other platforms and therefore can only be used for iOS devices. Problems occure with Windows Phone too. Refering to the Windows Phone documentation, it should be possible to connect with other platforms. However there are no good sample implementation for accomplishing this goal. In general the wifi direct technologie is not mature on Windows Phone. Only Android could satify the needs. An implementation of a wifi direct prototype could be accomplisheda and a connection with a Raspberry pi could be generated.

\section{Wifi direct}
\label{sec:WifiDirect}
The field study of wifi direct is very new. In case of the Raspberry Pi prototype, there were not much sources to get infromation on how to setup a wifi direct connection successfully. Even the Realtek P2P UI console application did not work reliably. For Android wifi direct will be supported since Android 4.0. However the hardware manufacturer have the final say to enable this feature. 

